---
title: "Final Project Wengran Xiao"
output: html_document
date: "2022-12-07"
---

## My topic
The purpose of this project is to find the relationship between the number of infant death and the GDP per capita of each country. Theoretically, a country with low GDP per capital has less health resources, low-quality food, heavier workload and low medical techniques for the population, which will lead to more infant death.


## Initialize two datasets
There are two original datasets used for the project. The file data1 has a series of life expectancy data of different years of all the countries in the world. The file data2 has the GDP data of different years of countries. 

```{r}
library(dplyr)
library(ggplot2)
library(skimr)
library(moderndive)
library(infer)
library(tidyr)
```

```{r}
data1<-read.csv("/Users/wengranxiao/Desktop/SI544/final_project/Life_Expectancy_Data.csv")

data2<- read.csv("/Users/wengranxiao/Desktop/SI544/final_project/GDP.csv")
```


## Wrangling the data
Only infant death of the Year 2014 and 2015 is needed and the GDP of 2015 is needed, so the two original charts should be wrangled and combined together.

```{r}
data1 <-data1 %>%
  filter(Year=="2015"|Year=="2014")%>%
  select(Country,infant.deaths,Year)
```

```{r}
data2 <- data2 %>%
  select(Country,X2015) %>%
  rename(GDP=X2015)
```

```{r}
finaldata <- data1 %>%
  inner_join(data2,by="Country")
```

## Descriptive statistics
Below are some descriptive statistics of the finaldata to help better understand the dataset.

```{r}
# Mean and median 
mean_death <-mean(finaldata$infant.deaths)
mean_death

median_death <-median(finaldata$infant.deaths)
median_death
```
```{r}
# 25th and 75th percentile 
pct_25 <-quantile(finaldata$infant.deaths,0.25)
pct_25

pct_75 <-quantile(finaldata$infant.deaths,0.75)
pct_75
```
```{r}
# Range of infant death
max(finaldata$infant.deaths)-min(finaldata$infant.deaths)

```
```{r}
# Draw a histogram to visualize the distribution of infant death
# It shows that the majority of the infant death locates in zero.

ggplot(finaldata, mapping=aes(x=infant.deaths))+
  geom_histogram()
  
```


## Fit linear model
To better understand and visualize the relationship between infant death and GDP of a country, firstly I draw a scatterplot and draw a linear. It seems when GDP increases, the death decreases.

```{r}
ggplot(finaldata, aes(y = infant.deaths, x = GDP))+
  geom_point()+
  geom_smooth(method="lm")
  
```


## Interpret the linear model
Then I get a regression table to interpret the linear model. As shown in the regression table, "infant.death=-0.001*GDP+39.439". This means when GDP increases by 1, the infant death will decrease by 0.001. 

```{r}
reg_model <- lm(infant.deaths ~ GDP, data=finaldata)
get_regression_table(reg_model)

```

## See the goodness of the linear model by r2
To test the effectiveness of the linear model, I then calculate the r-square. The r2 is 0.029, which is a very small number, so this is not a good linear model.

```{r}
get_regression_summaries(reg_model)
```

## Conclusion
We can say that infant death and the GDP per capita of a country has certain relationship, but it cannot be perfectly interpreted by linear model.




